\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}
Cost and effort estimation is a critical part of any major project. A wrong estimate can lead to a catastrophic failure. According to a survey, over 60\% of all software projects fail to complete within their estimated cost and time budget. On top of that, our methods for calculating the cost and effort of a software project are not very accurate. Most of the organizations make project managers calculate the current project's cost and effort by comparing it to a similar project they have completed before. This method is flawed since it assumes that the features of the project are excatly the same as the features of the previous projects. This is obviously not true as different project have different features that are driven from their scope, industry, and other factors. We aspire to develop system that can introduce new and far better solutions to the problem of cost and effort estimation. Our system will provide many ways of estimating effort including custom machine learning techniques, traditdional mathematical methods as well as providing a platform to make manual estimations and discussion between experts and managers, easier and seamless.

\newpage


\section*{Dedication}
\addcontentsline{toc}{section}{Dedication}
We dedicate this work to our parents who always supported us in everything and in every condition,
our teacher who never fails to teach and guide us, to administrators of Software Engineering
Department for their help and support throughout the degree.

\newpage


\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}
In the name of Allah, the Most Gracious and the Most Merciful. All praises to Allah and His blessing
for the completion of this project. We thank Allah for all the opportunities, trials and strength that
have been showered on me to finish this project. We experienced so much during this process, not
only from the academic aspect but also from the aspect of personality. My humblest gratitude to the
holy Prophet Muhammad (Peace be upon him) whose way of life has been a continuous guidance for
me.


We feel highly privileged in taking this opportunity to express our heartiest gratitude to my
respective project supervisor Dr. Yasir Mehmood, Department of Software Engineering, The
University of Lahore, for his dexterous supervision, inspiring and impetuous guidance, valuable
suggestions, technical help and mostly his scolding to complete this research study as well as for
writing this dissertation.


Our deepest gratitude goes to all of our family members. It would not be possible to write this thesis
without the support from them. We also want to extend my thanks to Admin Staff in the Faculty of
Software Engineering Department, University of Lahore, for their help and support in the
administrative works.


May God shower the above cited personalities with success and honour in their life.

\newpage

