\section{Lesson Learnt and Future Enhancements}

\vspace{20mm}


\Huge{\textbf{Lesson Learnt and Future Enhancements}}

\vspace{20mm}


\begin{abstract}

    In this chapter we will discuss the lessons learnt and future enhancements of the system.
    The lessons learnt will be discussed in the form of a list of problems and the future enhancements
    will be discussed in the form of a list of ideas.



\end{abstract}

\vspace{20mm}

\large{\textbf{Outline}}

\begin{center}
    \begin{itemize}
        \item Lesson Learnt
        \item Future Enhancements
    \end{itemize}
\end{center}
\pagebreak


% Lesson Learnt
\subsection{Lesson Learnt}

Everything in EffortAero, especially programming, takes longer than you expect.
Even if everything goes smoothly, it's difficult to predict how
long a feature will take. As we began working on it and determined
its specs and features, we realised that it was a significant project
and that we needed to begin working on it sooner. We learned how to
manage a project with a Two-person team, how to manage time, and
how to handle specifications.
Before you test the entire, test the components. Parts that have been
thoroughly tested save time. Integrating separate pieces can be difficult,
for example, due to mismatched or misunderstanding interfaces between modules.
It becomes much easier to trace down integration issues if you can trust
that the parts perform as planned.

% Future Enhancements
\subsection{Future Enhancements}
Firstly, we will deploy the system to a production environment.
We will then test the system in the production environment.
From the feedback we will determine what we should do to improve the system.
So then we will decide to add more functionality to the system such as:
\begin{itemize}
    \item Adding Manager as well as Developer to the system from outsource company.
    \item You will hire any developer you want like as Fiverr.
    \item You will hire any manager you want like as Fiverr.
    \item Adding NLP to determine the UCP if user can add the UCP in form of JPG or PNG.
    \item We will shift our Database as centralised database or distributed database.
\end{itemize}
