\section{Summary and Conclusions}

\vspace{20mm}


\Huge{\textbf{Summary and Conclusions}}

\vspace{20mm}


\begin{abstract}

    This chapter is dedicated to representing the Summary and Conclusions of the system.
    In first of this chapter we will sumarize the system and the system's features.
    In second of this chapter we will discuss about system's conclusions and outcomes.



\end{abstract}

\vspace{20mm}

\large{\textbf{Outline}}

\begin{center}
    \begin{itemize}
        \item Summary
        \item Conclusion
    \end{itemize}
\end{center}
\pagebreak


% Summary
\subsection{Summary}
The proposed system aspires to revolutionize and update the methodologies of software cost and effort
estimation. This particular area of software engineering hasn’t been worked on in order to create an
effective and usable system. The Proposed system implements state of the art machine learning algorithms
to give personalized and highly accurate estimations to all sorts of software projects. This accuracy is
achieved by training the model on modern datasets collected from actual software development companies
of successfully completed projects.This system will provide multiple methods to calculate estimates such
as the Delphi Technique, UCP Technique and Machine Learning techniques.
Along with the automated cost estimation services, the system will also provide a platform to collaborate
with developers and managers to discuss and agree on a better estimate. This platform is implemented to
enable the use of manual estimation techniques like Delphi.
The system can help software development companies save millions of dollars as well as countless hours
of time, spent on the cost and effort estimation process. This will enable faster development and better
software quality.
% Conclusion
\subsection{Conclusion}
At the end of the complete development of the project we have a web Application that can be used by
anyone to estimate the cost of any software project. The system is a used as a tool to estimate the
cost of any software project with three different methods which are Delphi Technique, UCP Technique and
Machine Learning techniques. If you want to use the system, you can signup the application from the
link and do the estimation.
Our Application is basically for Software Development Companies to estimate the cost of their projects.
The system is a used as a tool to estimate the cost of any software project by the companies's manager and manager
will create a project and add the developer to the project which will provide the esimation of the modules as well as
the whole system. The system will also provide a platform to collaborate with developers and managers to discuss and agree on a better estimate.
The system can help software development companies save millions of dollars as well as countless hours of time, spent on the cost and effort estimation process.
This will enable faster development and better software quality.
